---
title: "AdviseInvest Data Exercise Answer Key"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```

## Get Data


```{r}
d <- read_csv("adviseinvest_dirty.csv")

glimpse(d)

summary(d)
```


Here is a data dictionary:

- ANSWERED: Indicator for whether the call was answered.
- INCOME:  Annual income of customer
- FEMALE: Indicator for whether the customer is female
- AGE:  Age of customer
- JOB:  Indicator for  job type.
- NUM_DEPENDENTS:  Number of dependents.
- RENT:  Indicator for whether customer rents
- OWN_RES:  Indicator for whether  customer owns residence
- NEW_CAR:  Indicator of whether the  customer owns a new car
- CHK_ACCT: Number of checking accounts
- SAV_ACCT: Number of savings accounts
- NUM_ACCTS:  Total number of   other accounts
- MOBILE:  Indicator for whether the call back number is mobile
- PRODUCT:  Type of product purchased. (0 represents no purchase)

## Clean data

### Create factors

```{r}
d <- d %>%
  mutate(job = factor(job),
         product = factor(product))
```

### Filter out rows with mistaken data

```{r}
d <- d %>%
  filter(income > 0,
         num_accts < 5,
         !is.na(new_car))

summary(d)
```

## Explore data

1. Mean of Answered

```{r}
mean(d$answered)
```

2. Plot chk_acct against answered.

```{r}
d %>%
  mutate(answered = factor(answered)) %>%
  ggplot(aes(answered, chk_acct)) + 
  geom_boxplot()
```

3. Plot of mobile against answered.

```{r}
d %>%
  mutate(answered = factor(answered),
         mobile = factor(mobile)) %>%
  group_by(mobile, answered) %>%
  count() %>%
  group_by(answered) %>%
  mutate(proportion = n / sum(n)) %>%
  ggplot(aes(mobile, proportion, fill = answered)) + 
  geom_bar(stat="identity", position = "dodge")
```
