---
title: "Project-Model Evaluation and Deployment RMarkdown Template"
author: ""
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rpart)
library(rpart.plot)
library(magrittr)

```

Note:  

- Change the information in the yaml header above:  title and author
- Make sure output is html_document.
- Once you are finished coding, run each chunk individually to make sure there are no errors.  (If necessary fix your code.) Once your code is error-free, click "knit" on the menu above. Your document should compile to HTML, provided that you have output set to "html_document."
- In the code chunk above ("setup"), echo is set to TRUE.  This means that the code in your chunks will be displayed, along with the results, in your compiled document.


## Load and Transform Data


```{r}

```

## Fit model


```{r}

```

## Questions

### Q1


```{r}

```

### Q2

```{r}

```


### Q3


```{r}

```

### Q4


```{r}

```


### Q5


### Q6

```{r}

```

