---
title: "Project: Modeling with Classification Trees RMarkdown Template"
author: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rpart)
library(rpart.plot)

```

Note:  

- Change the information in the yaml header above:  title and author.
- Make sure output is html_document.
- Once you are finished coding, run each chunk individually to make sure there are no errors.  (If necessary fix your code.) Once your code is error-free, click "knit" on the menu above. Your document should compile to HTML, provided that you have output set to "html_document."
- In the code chunk above ("setup") echo is set to TRUE.  This means that the code in your chunks will be displayed, along with the results, in your compiled document.

## Load and Transform Data

Here is a data dictionary:

- ANSWERED: Indicator for whether the call was answered.
- INCOME:  Annual income of customer
- FEMALE: Indicator for whether the customer is female
- AGE:  Age of customer
- JOB:  Indicator for  job type.
- NUM_DEPENDENTS:  Number of dependents.
- RENT:  Indicator for whether customer rents
- OWN_RES:  Indicator for whether  customer owns residence
- NEW_CAR:  Indicator of whether the  customer owns a new car
- CHK_ACCT: Number of checking accounts
- SAV_ACCT: Number of savings accounts
- NUM_ACCTS:  Total number of   other accounts
- MOBILE:  Indicator for whether the call back number is mobile
- PRODUCT:  Type of product purchased. (0 represents no purchase)

```{r}
d <- read_csv("adviseinvest_clean.csv")  %>%
  select(-product) %>% 
  mutate(answered = factor(ifelse(answered==0, "no","yes")),
         female = factor(female),
         job = factor(job),
         rent = factor(rent),
         own_res = factor(own_res),
         new_car = factor(new_car),
         mobile = factor(mobile)) 

```




## Questions

### Q1.  

```{r}

```

### Q2.  

```{r}

```

### Q3.  

```{r}


```

### Q4. 

```{r}

```

### Q5.


```{r}

```


### Q6. 

```{r}

```

### Q7. 

```{r}

```

### Q8. 

```{r}

```

